Contracts for Contracts

### 2023-05-02 paper/contract_solidity.tex
update some examples for section 2.2

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  # {y | y > x + 1}
  function f(uint x) returns (uint y) { ... }
\end{lstlisting}
It is also equivalent to core syntax:
\begin{lstlisting}
  # {x | x > 0} -> {y | y > x + 1}
\end{lstlisting}

@@

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  function f(uint x) returns (uint y) { ... }
\end{lstlisting}
It is equivalent to core syntax where the omitted part is simply \code{true}:

\begin{lstlisting}
  # {x | x > 0} -> {y | true}
\end{lstlisting}
Another way is to use the `any` flat contract, which is defined as
\code{any = { _ | true }}:
\begin{lstlisting}
  # {x | x > 0} -> any
\end{lstlisting}

For multi-argument functions, we use multiple \code{->} to compose larger function
contracts:
\begin{lstlisting}
  # {x | x > 0} -> {y | y < 100} -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}
Or, we could write a single flat contract for the argument introducing
multiple argument binders:
\begin{lstlisting}
  # { (x, y) | x > 0 && y < 100 } -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}

>>>>

% \begin{lstlisting}[language=Solidity]
%   # {x | x > 0}
%   # {y | y > x + 1}
%   function f(uint x) returns (uint y) { ... }
% \end{lstlisting}

\begin{lstlisting}[language=Solidity]
  # {x | x % 1e18 < 1e17}
  # {y | y < type(uint).max / 1e18}
  function toEther(uint x) returns (uint y) { ... }
\end{lstlisting}

It is also equivalent to core syntax:
% \begin{lstlisting}
%   # {x | x > 0} -> {y | y > x + 1}
% \end{lstlisting}

\begin{lstlisting}[language=Solidity]
  # {x | x % 1e18 < 1e17} -> {y | y < type(uint).max / 1e18}
  function toEther(uint x) returns (uint y) { ... }
\end{lstlisting}

@@

% \begin{lstlisting}[language=Solidity]
%   # {x | x > 0}
%   function f(uint x) returns (uint y) { ... }
% \end{lstlisting}

\begin{lstlisting}[language=Solidity]
  # {x | x < type(uint).max / 1e18}
  function toWei(uint x) returns (uint y) { ... }
\end{lstlisting}

It is equivalent to core syntax where the omitted part is simply \code{true}:

\begin{lstlisting}[language=Solidity]
  # {x | x < type(uint).max / 1e18} -> {y | true}
\end{lstlisting}

Another way is to use the `any` flat contract, which is defined as
\code{any = { _ | true }}:
\begin{lstlisting}
  # {x | x < type(uint).max / 1e18} -> any
\end{lstlisting}

For multi-argument functions, we use multiple \code{->} to compose larger function
contracts:

\begin{lstlisting}
  # {x | x > 0} -> {y | y < 100} -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}

% \begin{lstlisting}[language=Solidity]
% # {rate | rate > 0 && rate < 100}
% # {time | time != 0}
% function simpleInterest(uint principle, uint rate, uint time) returns (uint interest) { ... }
% \end{lstlisting}

Or, we could write a single flat contract for the argument introducing
multiple argument binders:

\begin{lstlisting}
  # { (x, y) | x > 0 && y < 100 } -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}
